---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


# Loading and preprocessing the data

library(readr)
dataset <- read_csv("C:/Users/Aline/Dropbox/QSS course/Coursera/Data/activity/activity.csv")

View(dataset)

## What is mean total number of steps taken per day?

For this part of the assignment,I will ignore the missing values in the dataset.



```{r echo=TRUE}
library(tidyverse)
library(lattice)

dataset$date <- as.Date(dataset$date, "%Y-%m-%d")

totalossteps <- aggregate(steps ~ date, data = dataset, sum, na.rm = TRUE)

hist(totalossteps$steps, main = "Total steps", xlab = "", col = "green")

```

I will now make a histogram of the total number of steps taken each day.


Then, I calculate and report the mean and median total number of steps taken per day.


```{r echo=TRUE}

mean(totalossteps$steps, na.rm = TRUE)
median(totalossteps$steps, na.rm=TRUE)

```

## What is the average daily activity pattern?

To answer this quertion, I first make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis).

```{r echo=TRUE}

time_series <- tapply(dataset$steps, dataset$interval, mean, na.rm = TRUE)

plot(row.names(time_series), time_series, type = "l", xlab = "5 minutes interval", 
    ylab = "", main = "Number of steps taken - average", 
    col = "blue")
```


Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
max_interval <- which.max(time_series)
names(max_interval)
```


## Imputing missing values

```{r}
activity_NA <- sum(is.na(dataset))
activity_NA
```

I'm uncertain how to continue.

## Are there differences in activity patterns between weekdays and weekends?

Im uncertain how to do this.
